SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-10 sedona-ieice16/revision/resources/paper_black.tex
Modified Revision of SEDONA

\begin{summary}
{\color{blue}
Measuring program execution time is 
a \hbox{much-used} technique for performance evaluation in computer science. 
Without proper care, however, timed results may vary a lot, 
thus making it hard to trust their validity. 
In this paper we propose a novel timing protocol to significantly 
reduce such variability.
}

@@

Measuring program execution time is a much-used
technique for performance evaluation in computer science. 
Despite the importance of accurate and precise execution-time measurement, 
how to achieve {\em better} timing has not been well addressed. 
Surprisingly, there is considerable variability in the measured time.
{\color{blue}
The goal of this paper is to propose
a better timing protocol that can significantly reduce such variability 
and thus enable better timing results without a doubt of their validity.
}

Consider a simple compute-bound program, what we term {\em PUT} (program-under-test), 
as shown in Fig.~\ref{alg:put}. 
This program runs a nested for-loop with a specified task length ($tl$) (in seconds). 
{\color{blue}
The $tl$ value is used to compute 
the number of iterations ($t$) for which that for-loop is performed 
to reach the specified task length.}

@@

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. 
{\color{blue}
Note that PUT128 was run on a machine, with 
a specification illustrated in Table~\ref{tab:machine_config}, 
in the same timing environment as used in our prior work~\cite{Currim}, 
with (i)~non-critical daemons deactivated, 
(ii)~the Network Timing Protocol daemon switched on,  
(iii)~particular CPU features~\cite{intel15,intelSpeed15} turned off, 
and (iv)~an up-to-date kernel installed.

@@

{\bf Characteristics.} There are several important specifics of our protocol. 
First, we utilize {\em process time} (PT) rather than on elapsed time (ET). 
The use of PT is preferred, as it takes into account 
the time taken for only a ``process'' (or program) of interest.
PT is defined as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode. 
These tick measures are obtainable via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}. 
Second, the protocol throws out some executions that involve
{\em infrequent, \hbox{long-running} daemon processes}. 
We observe that such daemon processes substantially impact 
the execution time of the process.  
By eliminating those executions, the protocol greatly improves
the overall measurement quality, which would otherwise be biased by them.
}

@@

\begin{figure}[t]
	\centering
	\subfigure[{\color{blue}Initial Elapsed Time Measurement}]{
		\includegraphics[width=0.224\textwidth]{128_sec_et_old.eps}
		\label{fig:hist_before_et}
	}
	\subfigure[{\color{blue}Program Time After Our Protocol}]{
		\includegraphics[width=0.224\textwidth]{128_sec_pt_new.eps}
		\label{fig:hist_after_pt}
	}
	\caption{{\color{blue}An Example of Measurement Results on a \linebreak \hbox{Compute-bound} 
	Program-Under-Test}~\label{fig:meas_comp}}
	\vspace{-.18in}
\end{figure}

@@

{\color{blue}
\item We evaluate the performance of the protocol with rigorous experiments 
using real-world programs.
}

@@

\noindent
{\color{blue}
The rest is organized as follows. 
We next elaborate on the proposed timing protocol. In turn we evaluate the performance of the scheme using real workloads. 
}

@@

In this section we propose a novel execution time measurement scheme, 
called {\em SEDONA} (Selective Elimination through Detection of infrequent, lOng-ruNning dAemons). 
{\color{blue}
Our scheme (1) utilizes PT (process time) to avoid absorbing timing noise from other co-running processes and (2)~identifies and eliminates executions including daemon processes that are infrequent and \hbox{long-running} via a {\em cutoff} measure. 
}

Our SEDONA protocol consists of a total of ten steps, as described in Fig.~\ref{alg:find}.
{\color{blue} 
Note that this protocol (algorithm) is applicable to any arbitrary Linux system.}

@@

{\bf A Running Example.} 
{\color{blue}
First, we set up the same measurement environment as described earlier in \hbox{Section}~\ref{sec:intro}, 
to eliminate known timing factors (Step~1).
}

@@

{\color{blue}
To identify such daemons, we use a novel \hbox{scatter} plot: 
those of {\em pairs of successive samples}. 
So samples~\#{1} and~\#{2} form the first pair and samples~\#{3} and~\#{4} 
form the second pair.
Such a pair is termed ``\hbox{{\it dual-PUT}}.'' 
A sample of \hbox{dual-PUT256}, for instance, 
consists of two consecutive (odd and even) 
samples of PUT128: 
sample~\#{1} of dual-PUT256 is equivalent 
to samples~\#{1} and~\#{2} of PUT128.
}

Fig.~\ref{fig:raw_put128} presents such a scatter plot 
of 400 samples of a run of \hbox{dual-PUT256} constructed 
from a run of the 800 PUT128 samples (Step~3). 
{\color{blue}
The $xy$-plane corresponds to the dual-PUT samples. 
For example, \hbox{sample}~\#{2} of a run of dual-PUT256 
is plotted as a point with samples~\#{3} and~\#{4} of a run of PUT128 
on the respective $x$ and $y$ axes. In that sense 
the $x$ ($y$) axis is named as ``Odd (Even) Sample's ET.''
}
There are two quite obvious outliers with ETs 
of 163,913 ms (rightmost) and 161,785 ms (uppermost), respectively.

@@

In Step~6 we identify, for each daemon in the \hbox{$L$-samples}, 
those that are actual long-running daemon
executions.  We define such executions as those whose PT 
is over two standard deviations above the maximum PT for
that daemon in the central cluster samples. 
In the running example  {\tt flush-9:0}, 
{\tt jbd2/md0-8}, and {\tt md0\_raid1} 
are determined as infrequent, \hbox{long-running}.
{\color{blue}
We also identify ``extra'' infrequent daemons: 
{\tt bash}, {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
{\tt rhsmcertd-worke}, and {\tt sshd}, those 
found only in the $L$-samples but not in the central cluster.

For each of the infrequent daemons 
we use a heuristic to determine the daemon's periodicity:
the daemon must occur regularly in a sequence of samples.
For instance, {\tt rhn\_check} appears 
roughly every 112 samples (or almost every four hours). 
Four others ({\tt flush-9:0}, {\tt jbd2/md0-8}, {\tt md0\_raid1}, and {\tt rhn\_check}) 
all occur together and have a periodicity of about every 559 samples 
(5x longer, or just about 20 hours). 
}

@@

In Step 8 we repeat Steps 1--6, but instead with the much-longer running
PUT16384 (4.5 hours per \hbox{sample} versus 2 minutes), to see 
if any of our identified \hbox{infrequent} daemons are actually frequent 
at that much longer PUT execution time. 
We find some frequent daemon processes appearing in both of the 
clusters of \hbox{dual-PUT256} and \hbox{dual-PUT32768}{\color{blue}, each consisting of 
pairs of two successive samples of PUT128 and PUT16384.}
That said, the central cluster also contains other
  processes not seen in the \hbox{dual-PUT256} central cluster: 
  {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
  {\tt rhsmcertd-worke}, and {\tt sshd}. 
  But these daemons were categorized in the \hbox{dual-PUT256} analysis as {\em
  infrequent}, several having \hbox{periodicities} estimated at four or twenty hours.
{\color{blue}
When PUT128 had a ``short'' 
program time (or, two minutes), daemons with a periodicity of
hours are \hbox{infrequent}. But with PUT16384 
with a ``long'' program time (or, 4.5 hours),} 
some of those daemons are now frequent, and appear in the central cluster.

In Step~9 we compute 
the cutoff for each of those infrequent, long-running daemons so
identified, based on {\color{blue}the runs of PUT128 and 
PUT16384} as collected in Tab.~\ref{tab:final_infrequent_cutoff}. 
Here is how to compute the cutoff. For the cutoff of such a daemon with PUT128, 
we take the \hbox{midpoint} between the maximum of that daemon's PTs in the 
central cluster (or 0, if absent) and the \hbox{minimum} of those in the $L$-samples. 
For the cutoff of such a daemon with PUT16384, we do the same. 
We then compute a ``task time'' as 5\% of the inferred periodicity. 
This 5\% ensures that such infrequent daemons will impact 
only a small percentage of the shorter PUTs, while presumably being 
associated with much larger cutoffs for the very long PUTs. 
We also include daemons that (a)~were identified as infrequent and 
\hbox{long-running} from PUT128 and (b)~were not identified as so in the PUT16384 
\hbox{$L$-samples}, but may have in the \hbox{dual-PUT32768} central cluster.
We then take the {\em maximum} of the two cutoffs for the final cutoff PT 
(the last column of Tab.~\ref{tab:final_infrequent_cutoff}).

@@

{\color{blue}
First, we compared the performance of the two approaches 
using real-world programs such as insertion sort, termed SORT and 
matrix multiplication (in column major), termed MM. 
In this comparison SEDONA outperformed ORG, as can be seen in Fig.~\ref{fig:synprog_test}. 
As workload size increased, the performance gap between the two 
were increasingly widened, reaching up to by 6x.
}

\vspace{-.2in}
\begin{figure}[h]
	\centering
	\subfigure[{\color{blue}SORT - Standard Deviation}]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[{\color{blue}MM - Standard Deviation}]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	\vspace{-.1in}
	\caption{Performance Comparison on Real-world Programs~\label{fig:synprog_test}}
\vspace{-.25in}
\end{figure}

@@

{\color{blue}
Table~\ref{tab:spec_real} shows that 
SEDONA bettered ORG,
on the standard deviation and relative error across the very different SPEC benchmarks. 
To be more specific, all the benchmarks revealed a smaller standard deviation 
from SEDONA as compared to that of ORG. 
Our timing protocol quite effectively filtered out infrequent daemon executions 
in the industrial workloads. The relative error of SEDONA was also 
lower than that of ORG for almost every benchmark.
For example, about a 10x \hbox{margin} between the two resulted from {\tt 434}.
}

SEDONA also scaled well for the SPEC workloads, 
with regard to growth of relative error as the execution time lengthened.
For the short benchmarks 
(e.g. {\tt 400}, {\tt 403}, {\tt 410}, 
{\tt 434}, {\tt 445}, and {\tt 999}: those taking \hbox{under} 100 sec), 
our scheme outperformed the ORG method by about 3.5x, on average. 
The SEDONA protocol continued its dominance against the conventional technique 
for the medium-length benchmarks (e.g. {\tt 447}, {\tt 456}, {\tt 470}, and {\tt 473}).
{\color{blue}
Even for the long-running benchmarks (e.g. {\tt 416}, {\tt 436}, and {\tt 454}, both $>$1,000 sec), 
the relative error of \hbox{SEDONA} was still lower than that of ORG.
}

To summarize, our proposed SEDONA protocol can achieve {\em better} accuracy,
precision, and scalability in measuring the execution time of real \hbox{compute-bound} programs 
than the ET-based existing method. 
{\color{blue}
The experimental results demonstrate 
the general applicability of SEDONA to timing any CPU-bound program.}

%\vspace{-0.in}
\begin{table}[t]
\centering
{
\tiny
\begin{tabular}{|p{0.1cm}|R{1.1cm}|R{1.1cm}|R{0.6cm}|R{0.6cm}|R{0.92cm}|R{0.92cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative Error}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SED.}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{{\tiny}}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SED.}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SED.}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {\color{blue}{75}} & {\color{blue}{7}} & {{\color{blue}5$\times$10$^{-3}$}} & {{\color{blue}5$\times$10$^{-4}$}}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}

{\color{blue}
\section{Conclusion}
\label{sec:conclusion}
\vspace{-0.07in}
We proposed a novel timing protocol called {\em SEDONA}, and 
performed an empirical evaluation to show that 
it is more precise and accurate than the extant method.}

>>>>

\begin{summary}
Measuring program execution time is 
a \hbox{much-used} technique for performance evaluation in computer science. 
Without proper care, however, timed results may vary a lot, 
thus making it hard to trust their validity. 
In this paper we propose a novel timing protocol to significantly 
reduce such variability.

@@

Measuring program execution time is a much-used
technique for performance evaluation in computer science. 
Despite the importance of accurate and precise execution-time measurement, 
how to achieve {\em better} timing has not been well addressed. 
Surprisingly, there is considerable variability in the measured time.
The goal of this paper is to propose
a better timing protocol that can significantly reduce such variability 
and thus enable better timing results without a doubt of their validity.

Consider a simple compute-bound program, what we term {\em PUT} (program-under-test), 
as shown in Fig.~\ref{alg:put}. 
This program runs a nested for-loop with a specified task length ($tl$) (in seconds). 
The $tl$ value is used to compute 
the number of iterations ($t$) for which that for-loop is performed 
to reach the specified task length.

@@

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. 
Note that PUT128 was run on a machine, with 
a specification illustrated in Table~\ref{tab:machine_config}, 
in the same timing environment as used in our prior work~\cite{Currim}, 
with (i)~non-critical daemons deactivated, 
(ii)~the Network Timing Protocol daemon switched on,  
(iii)~particular CPU features~\cite{intel15,intelSpeed15} turned off, 
and (iv)~an up-to-date kernel installed.

@@

{\bf Characteristics.} There are several important specifics of our protocol. 
First, we utilize {\em process time} (PT) rather than on elapsed time (ET). 
The use of PT is preferred, as it takes into account 
the time taken for only a ``process'' (or program) of interest.
PT is defined as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode. 
These tick measures are obtainable via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}. 
Second, the protocol throws out some executions that involve
{\em infrequent, \hbox{long-running} daemon processes}. 
We observe that such daemon processes substantially impact 
the execution time of the process.  
By eliminating those executions, the protocol greatly improves
the overall measurement quality, which would otherwise be biased by them.

@@

\begin{figure}[t]
	\centering
	\subfigure[Initial Elapsed Time Measurement]{
		\includegraphics[width=0.224\textwidth]{128_sec_et_old.eps}
		\label{fig:hist_before_et}
	}
	\subfigure[Program Time After Our Protocol]{
		\includegraphics[width=0.224\textwidth]{128_sec_pt_new.eps}
		\label{fig:hist_after_pt}
	}
	\caption{An Example of Measurement Results on a \linebreak \hbox{Compute-bound} 
	Program-Under-Test~\label{fig:meas_comp}}
	\vspace{-.18in}
\end{figure}

@@

\item We evaluate the performance of the protocol with rigorous experiments 
using real-world programs.

@@

\noindent
The rest is organized as follows. 
We next elaborate on the proposed timing protocol. In turn we evaluate the performance of the scheme using real workloads.

@@

In this section we propose a novel execution time measurement scheme, 
called {\em SEDONA} (Selective Elimination through Detection of infrequent, lOng-ruNning dAemons). 
Our scheme (1) utilizes PT (process time) to avoid absorbing timing noise from other co-running processes and (2)~identifies and eliminates executions including daemon processes that are infrequent and \hbox{long-running} via a {\em cutoff} measure.

Our SEDONA protocol consists of a total of ten steps, as described in Fig.~\ref{alg:find}.
Note that this protocol (algorithm) is applicable to any arbitrary Linux system.

@@

{\bf A Running Example.} 
First, we set up the same measurement environment as described earlier in \hbox{Section}~\ref{sec:intro}, 
to eliminate known timing factors (Step~1).

@@

To identify such daemons, we use a novel \hbox{scatter} plot: 
those of {\em pairs of successive samples}. 
So samples~\#{1} and~\#{2} form the first pair and samples~\#{3} and~\#{4} 
form the second pair.
Such a pair is termed ``\hbox{{\it dual-PUT}}.'' 
A sample of \hbox{dual-PUT256}, for instance, 
consists of two consecutive (odd and even) 
samples of PUT128: 
sample~\#{1} of dual-PUT256 is equivalent 
to samples~\#{1} and~\#{2} of PUT128.

Fig.~\ref{fig:raw_put128} presents such a scatter plot 
of 400 samples of a run of \hbox{dual-PUT256} constructed 
from a run of the 800 PUT128 samples (Step~3). 
The $xy$-plane corresponds to the dual-PUT samples. 
For example, \hbox{sample}~\#{2} of a run of dual-PUT256 
is plotted as a point with samples~\#{3} and~\#{4} of a run of PUT128 
on the respective $x$ and $y$ axes. In that sense 
the $x$ ($y$) axis is named as ``Odd (Even) Sample's ET.''
There are two quite obvious outliers with ETs 
of 163,913 ms (rightmost) and 161,785 ms (uppermost), respectively.

@@

In Step~6 we identify, for each daemon in the \hbox{$L$-samples}, 
those that are actual long-running daemon
executions.  We define such executions as those whose PT 
is over two standard deviations above the maximum PT for
that daemon in the central cluster samples. 
In the running example  {\tt flush-9:0}, 
{\tt jbd2/md0-8}, and {\tt md0\_raid1} 
are determined as infrequent, \hbox{long-running}.
We also identify ``extra'' infrequent daemons: 
{\tt bash}, {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
{\tt rhsmcertd-worke}, and {\tt sshd}, those 
found only in the $L$-samples but not in the central cluster.

For each of the infrequent daemons 
we use a heuristic to determine the daemon's periodicity:
the daemon must occur regularly in a sequence of samples.
For instance, {\tt rhn\_check} appears 
roughly every 112 samples (or almost every four hours). 
Four others ({\tt flush-9:0}, {\tt jbd2/md0-8}, {\tt md0\_raid1}, and {\tt rhn\_check}) 
all occur together and have a periodicity of about every 559 samples 
(5x longer, or just about 20 hours).

@@

In Step 8 we repeat Steps 1--6, but instead with the much-longer running
PUT16384 (4.5 hours per \hbox{sample} versus 2 minutes), to see 
if any of our identified \hbox{infrequent} daemons are actually frequent 
at that much longer PUT execution time. 
We find some frequent daemon processes appearing in both of the 
clusters of \hbox{dual-PUT256} and \hbox{dual-PUT32768}, each consisting of 
pairs of two successive samples of PUT128 and PUT16384.
That said, the central cluster also contains other
  processes not seen in the \hbox{dual-PUT256} central cluster: 
  {\tt grep}, {\tt rhn\_check}, {\tt rhnsd}, {\tt rhsmcertd}, 
  {\tt rhsmcertd-worke}, and {\tt sshd}. 
  But these daemons were categorized in the \hbox{dual-PUT256} analysis as {\em
  infrequent}, several having \hbox{periodicities} estimated at four or twenty hours.
When PUT128 had a ``short'' 
program time (or, two minutes), daemons with a periodicity of
hours are \hbox{infrequent}. But with PUT16384 
with a ``long'' program time (or, 4.5 hours),
some of those daemons are now frequent, and appear in the central cluster.

In Step~9 we compute 
the cutoff for each of those infrequent, long-running daemons so
identified, based on the runs of PUT128 and 
PUT16384 as collected in Tab.~\ref{tab:final_infrequent_cutoff}. 
Here is how to compute the cutoff. For the cutoff of such a daemon with PUT128, 
we take the \hbox{midpoint} between the maximum of that daemon's PTs in the 
central cluster (or 0, if absent) and the \hbox{minimum} of those in the $L$-samples. 
For the cutoff of such a daemon with PUT16384, we do the same. 
We then compute a ``task time'' as 5\% of the inferred periodicity. 
This 5\% ensures that such infrequent daemons will impact 
only a small percentage of the shorter PUTs, while presumably being 
associated with much larger cutoffs for the very long PUTs. 
We also include daemons that (a)~were identified as infrequent and 
\hbox{long-running} from PUT128 and (b)~were not identified as so in the PUT16384 
\hbox{$L$-samples}, but may have in the \hbox{dual-PUT32768} central cluster.
We then take the {\em maximum} of the two cutoffs for the final cutoff PT 
(the last column of Tab.~\ref{tab:final_infrequent_cutoff}).

@@

First, we compared the performance of the two approaches 
using real-world programs such as insertion sort, termed SORT and 
matrix multiplication (in column major), termed MM. 
In this comparison SEDONA outperformed ORG, as can be seen in Fig.~\ref{fig:synprog_test}. 
As workload size increased, the performance gap between the two 
were increasingly widened, reaching up to by 6x.

\vspace{-.2in}
\begin{figure}[h]
	\centering
	\subfigure[SORT - Standard Deviation]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[MM - Standard Deviation]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	\vspace{-.1in}
	\caption{Performance Comparison on Real-world Programs~\label{fig:synprog_test}}
\vspace{-.25in}
\end{figure}

@@

Table~\ref{tab:spec_real} shows that 
SEDONA bettered ORG,
on the standard deviation and relative error across the very different SPEC benchmarks. 
To be more specific, all the benchmarks revealed a smaller standard deviation 
from SEDONA as compared to that of ORG. 
Our timing protocol quite effectively filtered out infrequent daemon executions 
in the industrial workloads. The relative error of SEDONA was also 
lower than that of ORG for almost every benchmark.
For example, about a 10x \hbox{margin} between the two resulted from {\tt 434}.

SEDONA also scaled well for the SPEC workloads, 
with regard to growth of relative error as the execution time lengthened.
For the short benchmarks 
(e.g. {\tt 400}, {\tt 403}, {\tt 410}, 
{\tt 434}, {\tt 445}, and {\tt 999}: those taking \hbox{under} 100 sec), 
our scheme outperformed the ORG method by about 3.5x, on average. 
The SEDONA protocol continued its dominance against the conventional technique 
for the medium-length benchmarks (e.g. {\tt 447}, {\tt 456}, {\tt 470}, and {\tt 473}).
Even for the long-running benchmarks (e.g. {\tt 416}, {\tt 436}, and {\tt 454}, both $>$1,000 sec), 
the relative error of \hbox{SEDONA} was still lower than that of ORG.

To summarize, our proposed SEDONA protocol can achieve {\em better} accuracy,
precision, and scalability in measuring the execution time of real \hbox{compute-bound} programs 
than the ET-based existing method. 
The experimental results demonstrate 
the general applicability of SEDONA to timing any CPU-bound program.

%\vspace{-0.in}
\begin{table}[t]
\centering
{
\tiny
\begin{tabular}{|p{0.1cm}|R{1.1cm}|R{1.1cm}|R{0.6cm}|R{0.6cm}|R{0.92cm}|R{0.92cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative Error}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SED.}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{{\tiny}}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SED.}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SED.}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {75} & {7} & {5$\times$10$^{-3}$} & {5$\times$10$^{-4}$}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}

\section{Conclusion}
\label{sec:conclusion}
\vspace{-0.07in}
We proposed a novel timing protocol called {\em SEDONA}, and 
performed an empirical evaluation to show that 
it is more precise and accurate than the extant method.
